Bayesian exponential random graph modelling of KWL Burial network

### 2020-03-26 analysis/paper/paper.Rmd
add note

## ERGM model

Exponential Random Graph Models (ERGMs) are a family of statistical model for network analysis to 
describe the formation of ties in a network. In traditional statistical model for network, a dyad, the pair of nodes, is measured by the presence of a tie according to the attributes of the nodes or ties, where each predictor variable for forming a tie is measured separately. In contrast to traditional model where variables not interacting with each other, ERGMs assumes the formation of a tie is influenced by the presence or absence of other ties or attributes of nodes and ties (Robins et al. 2007). In a network using ERGMs, predictor variables, called "network statistics", are direct functions of the ties themselves that the probability of occurrence of the configuration of ties can be hypothesized (Morries et al. 2008). This approach enables networks to be constructed in a variety of assumption and contexts to model social network in the past using archaeological data (Amati et al. 2019).

@@

toturial: 
https://www.r-bloggers.com/ergm-tutorial/

@@

We used ergm package in R for the model specification. Every term in an ERGM must have an associated algorithm for computing its value for network (Morris et al. 2008). The terms we selected for nwtwork specification include:

@@

# some exploration
1. there is different statistics between weighted and unweighed ties

Here is an example of inline code `r x` in the middle of a sentence.

>>>>

## Exponential Random Graph Models

Exponential Random Graph Models (ERGMs) are a family of statistical model for network analysis to 
describe the formation of ties in a network. In traditional statistical model for network, a dyad, the pair of nodes, is measured by the presence of a tie according to the attributes of the nodes or ties, where each predictor variable for forming a tie is measured separately. In contrast to traditional model where variables not interacting with each other, ERGMs assumes the formation of a tie is influenced by the presence or absence of other ties or attributes of nodes and ties (Robins et al. 2007). In a network using ERGMs, predictor variables, called "network statistics", are direct functions of the ties themselves that the probability of occurrence of the configuration of ties can be hypothesized [@Morris2008]. This approach enables networks to be constructed in a variety of assumption and contexts to model social network in the past using archaeological data [@Amati2019].

@@

@@

We used ergm package in R for the model specification. Every term in an ERGM must have an associated algorithm for computing its value for network [@Morris2008]. The terms we selected for nwtwork specification include:

@@

inline code `r x` example
